---
title: "nsf_snowdepths_datawrangling"
output: html_document
date: "2024-08-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set Up

```{r}
library(tidyverse)
library(lterdatasampler)
library(dplyr)
library(ggplot2)
library(readr)
library(readxl)
library(lubridate)
library(plotly)
library(openxlsx)
library(plotly)
library(rstatix)
library(htmlwidgets)
library(RColorBrewer)
library(patchwork)
library(ggpubr)

setwd("/Volumes/wcnr-network/Research/Kampf/Private/field_data")
```

## Calling in Data

### Weather Station Data

```{r}
transb_wx_15min_r <- read_csv('nsf/trans_burned/trans_burned_wx_15min_r.csv') %>%
  #have to convert the datetime to MST, not UTC, if uploading a csv
  mutate(datetime = as.POSIXct(datetime, tz = 'MST'))

transub_wx_hourly_r <- read_csv('nsf/trans_unburned/trans_unburned_wx_hourly_r.csv') %>%
  #have to convert the datetime to MST, not UTC, if uploading a csv
  mutate(datetime = as.POSIXct(datetime, tz = 'MST'))

persb_wx_hourly_r <- read_csv('nsf/pers_burned/pers_burned_wx_hourly_r.csv') %>%
  #have to convert the datetime to MST, not UTC, if uploading a csv
  mutate(datetime = as.POSIXct(datetime, tz = 'MST'))

persb_wx_hourly_r <- read_csv('nsf/pers_burned/pers_burned_wx_hourly_r.csv') %>%
  #have to convert the datetime to MST, not UTC, if uploading a csv
  mutate(datetime = as.POSIXct(datetime, tz = 'MST'))

persub_wx_hourly_r <- read_csv('nsf/pers_unburned/pers_unburned_wx_hourly_r.csv') %>%
  #have to convert the datetime to MST, not UTC, if uploading a csv
  mutate(datetime = as.POSIXct(datetime, tz = 'MST'))
```

### Snow Camera Data

```{r}
#105E camera snow depths
dailymax105E_persb_snow <- read_csv('nsf/camera_snowdepths/2024_persb_lp_highmort_east_snowdepths.csv')

dailymax105E_transb_snow <- read_csv('nsf/camera_snowdepths/2024_105E_transb_snowdepths.csv')

dailymax105E_transub_snow <- read_csv('nsf/camera_snowdepths/2024_105E_transub_snowdepths.csv')
```

## Creating Snow depth-specific Dataframes

### Weather Station Snowdepth Data

```{r}
# creating a dataframe that is all of the weather station data including snow depths for the winter seasons 

#transitional 
full24_transb_snow_wxstation_data <- transb_wx_15min_r %>%
    #adding date and time columns
  mutate(
    date = as_date(datetime),
    time = format(datetime, "%H:%M:%S")) %>%
  #assigning a timezone then filtering to specific datetimestep for winter 2023-24
   mutate(datetime_mst = with_tz(datetime, tzone = "MST")) %>%
  filter(datetime_mst >= as.POSIXct("2023-11-16 00:00:00", tz = "MST") & 
         datetime_mst <= as.POSIXct("2024-06-05 00:00:00", tz = "MST")) %>%
    select(-datetime) %>%
    rename(datetime = datetime_mst) %>%
    select(datetime, date, time, SnowDepth_m)

full24_transub_snow_wxstation_data <- transub_wx_hourly_r %>%
  #adding date and time columns
  mutate(
    date = as_date(datetime),
    time = format(datetime, "%H:%M:%S")) %>%
  #assigning a timezone then filtering to specific datetimestep for winter 2023-24
   mutate(datetime_mst = with_tz(datetime, tzone = "MST")) %>%
  filter(datetime_mst >= as.POSIXct("2023-11-16 00:00:00", tz = "MST") & 
         datetime_mst <= as.POSIXct("2024-06-05 00:00:00", tz = "MST")) %>%
    select(-datetime) %>%
    rename(datetime = datetime_mst) %>%
    select(datetime, date, time, SnowDepth_m)

#persistent
full24_persb_snow_wxstation_data <- persb_wx_hourly_r %>%
  #adding date and time columns
  mutate(
    date = as_date(datetime),
    time = format(datetime, "%H:%M:%S")) %>%
  #assigning a timezone then filtering to specific datetimestep for winter 2023-24
   mutate(datetime_mst = with_tz(datetime, tzone = "MST")) %>%
  filter(datetime_mst >= as.POSIXct("2023-11-16 00:00:00", tz = "MST") & 
         datetime_mst <= as.POSIXct("2024-06-05 00:00:00", tz = "MST")) %>%
    select(-datetime) %>%
    rename(datetime = datetime_mst) %>%
    select(datetime, date, time, SnowDepth_m)

full24_persub_snow_wxstation_data <- persub_wx_hourly_r %>%
  #adding date and time columns
  mutate(
    date = as_date(datetime),
    time = format(datetime, "%H:%M:%S")) %>%
  #assigning a timezone then filtering to specific datetimestep for winter 2023-24
   mutate(datetime_mst = with_tz(datetime, tzone = "MST")) %>%
  filter(datetime_mst >= as.POSIXct("2023-11-16 00:00:00", tz = "MST") & 
         datetime_mst <= as.POSIXct("2024-06-05 00:00:00", tz = "MST")) %>%
    select(-datetime) %>%
    rename(datetime = datetime_mst) %>%
    select(datetime, date, time, SnowDepth_m)
```

```{r}
#daily maximum snow depth to compare to snow camera data

dailymax_transb_snow_wxstation <- full24_transb_snow_wxstation_data %>%
  group_by(date) %>%
  summarize(maxsnowdepth_m = max(SnowDepth_m)) %>%
  mutate(maxsnowdepth_cm = maxsnowdepth_m*100) %>%
  #adding in burn_status and zone columns
  mutate(burn_status = "burned", zone = "transitional")

dailymax_transub_snow_wxstation <- full24_transub_snow_wxstation_data %>%
  group_by(date) %>%
  summarize(maxsnowdepth_m = max(SnowDepth_m)) %>%
  mutate(maxsnowdepth_cm = maxsnowdepth_m*100) %>%
  mutate(burn_status = "unburned", zone = "transitional")

dailymax_persb_snow_wxstation <- full24_persb_snow_wxstation_data %>%
  group_by(date) %>%
  summarize(maxsnowdepth_m = max(SnowDepth_m)) %>%
  mutate(maxsnowdepth_cm = maxsnowdepth_m*100) %>%
  mutate(burn_status = "burned", zone = "persistent")

dailymax_persub_snow_wxstation <- full24_persub_snow_wxstation_data %>%
  group_by(date) %>%
  summarize(maxsnowdepth_m = max(SnowDepth_m)) %>%
  mutate(maxsnowdepth_cm = maxsnowdepth_m*100) %>%
  mutate(burn_status = "unburned", zone = "persistent")
```

### Snow Camera Snowdepth Data

\*\* don't have the following dataframe for persistent unburned because that camera did not work.

```{r}
#manipulating dataframes to match weather station dataframes, etc.

dailymax105E_persb_snow <- dailymax105E_persb_snow %>%
  #make date recognized as a date
  mutate(date = as.Date(date)) %>%
  mutate(maxsnowdepth_m = max_depth_cm/100) %>%
  #renameing mac depth column 
  rename(maxsnowdepth_cm = max_depth_cm) %>%
  #selecting only the rows I need
  select(date, zone, burn_status, mortality, conditions, maxsnowdepth_m, maxsnowdepth_cm)

dailymax105E_transb_snow <- dailymax105E_transb_snow %>%
  #make date recognized as a date
  mutate(date = as.Date(date)) %>%
  mutate(maxsnowdepth_m = max_depth_cm/100) %>%
  #renameing mac depth column 
  rename(maxsnowdepth_cm = max_depth_cm) %>%
  #selecting only the rows I need
  select(date, zone, burn_status, mortality, conditions, maxsnowdepth_m, maxsnowdepth_cm)

dailymax105E_transub_snow <- dailymax105E_transub_snow %>%
  #make date recognized as a date
  mutate(date = as.Date(date)) %>%
  mutate(maxsnowdepth_m = max_depth_cm/100) %>%
  #renameing mac depth column 
  rename(maxsnowdepth_cm = max_depth_cm) %>%
  #selecting only the rows I need
  select(date, zone, burn_status, mortality, conditions, maxsnowdepth_m, maxsnowdepth_cm)
```

## Plotting Snowdepths 

```{r}
#colors for plots
#to display the colors
display.brewer.pal(n = 8, name = "Dark2")

#to get the hex number of the colors
brewer.pal(n = 8, name = "Dark2")
```

Plotting Persistent Weather Station & Snowstakes

```{r}
#persistent burned/unburned data weather station and snow camera data
dailypers_sd_plot <- ggplot() +
  geom_line(data = dailymax_persb_snow_wxstation, aes(x = date, y = maxsnowdepth_cm, color = "Pers Burned Wx Station")) + 
  geom_line(data = dailymax105E_persb_snow, aes(x = date, y = maxsnowdepth_cm, color = "Pers Burned Snowstake Camera")) +
  geom_line(data = dailymax_persub_snow_wxstation, aes(x= date, y = maxsnowdepth_cm, color =  "Pers Unburned Wx Station"), alpha = 0.7) +
  labs(
    #title = "Transitional Unburned",
    x = "Date",
    y = "Max Daily Snowdepth (cm)"
    ) +
  theme_bw() +
  scale_color_manual(values = c("Pers Burned Wx Station" = "#D95F02", "Pers Burned Snowstake Camera" = "#E6AB02", "Pers Unburned Wx Station" = "#66A61E"))

dailypers_sd_plot
```

Plotting Transitional Weather Station & Snowstakes

```{r}
dailytrans_sd_plot <- ggplot() +
  geom_line(data = dailymax_transb_snow_wxstation, aes(x = date, y = maxsnowdepth_cm, color = "Trans Burned Wx Station")) + 
  geom_line(data = dailymax105E_transb_snow, aes(x = date, y = maxsnowdepth_cm, color = "Trans Burned Snowstake Camera")) +
  geom_line(data = dailymax_transub_snow_wxstation, aes(x= date, y = maxsnowdepth_cm, color =  "Trans Unburned Wx Station"), alpha = 0.7) +
  geom_line(data = dailymax105E_transub_snow, aes(x= date, y = maxsnowdepth_cm, color =  "Trans Unburned Snowstake Camera"), alpha = 0.7) +
  labs(
    #title = "Transitional Unburned",
    x = "Date",
    y = "Max Daily Snowdepth (cm)"
    ) +
  theme_bw() +
  scale_color_manual(values = c("Trans Burned Wx Station" = "#D95F02", "Trans Burned Snowstake Camera" = "#E6AB02", "Trans Unburned Wx Station" = "#66A61E", "Trans Unburned Snowstake Camera"= "#7570B3"))

dailytrans_sd_plot
```

## Box Plots

Creating dataframes for boxplots

```{r}
#using the same dataframes as above, just adding a month column and filtering for feb-june
f_dailymax_persb_snow_wxstation <- dailymax_persb_snow_wxstation %>%
  #adding a month column
  mutate(month = month(date)) %>%
  select(date, month, zone, burn_status, everything()) %>%
  group_by(month) %>%
  mutate(mean_sd_bymonth_cm = mean(maxsnowdepth_cm)) %>%
  ungroup() %>%
  filter(month >= 2 & month <= 6)

f_dailymax_persub_snow_wxstation <- dailymax_persub_snow_wxstation %>%
  #adding a month column
  mutate(month = month(date)) %>%
  select(date, month, zone, burn_status, everything()) %>%
  group_by(month) %>%
  mutate(mean_sd_bymonth_cm = mean(maxsnowdepth_cm)) %>%
  ungroup() %>%
  filter(month >= 2 & month <= 6)

f_dailymax_transb_snow_wxstation <- dailymax_transb_snow_wxstation %>%
  #adding a month column
  mutate(month = month(date)) %>%
  select(date, month, zone, burn_status, everything()) %>%
  group_by(month) %>%
  mutate(mean_sd_bymonth_cm = mean(maxsnowdepth_cm)) %>%
  ungroup() %>%
  filter(month >= 2 & month <= 6)

f_dailymax_transub_snow_wxstation <- dailymax_transub_snow_wxstation %>%
  #adding a month column
  mutate(month = month(date)) %>%
  select(date, month, zone, burn_status, everything()) %>%
  group_by(month) %>%
  mutate(mean_sd_bymonth_cm = mean(maxsnowdepth_cm)) %>%
  ungroup() %>%
  filter(month >= 2 & month <= 6)

f_dailymax105E_persb_snow <- dailymax105E_persb_snow %>%
  #adding a month column
  mutate(month = month(date)) %>%
  select(date, month, zone, burn_status, everything()) %>%
  group_by(month) %>%
  mutate(mean_sd_bymonth_cm = mean(maxsnowdepth_cm)) %>%
  ungroup() %>%
  filter(month >= 2 & month <= 6)

f_dailymax105E_transb_snow <- dailymax105E_transb_snow %>%
  #adding a month column
  mutate(month = month(date)) %>%
  select(date, month, zone, burn_status, everything()) %>%
  group_by(month) %>%
  mutate(mean_sd_bymonth_cm = mean(maxsnowdepth_cm)) %>%
  ungroup() %>%
  filter(month >= 2 & month <= 6)

f_dailymax105E_transub_snow <- dailymax105E_transub_snow %>%
  #adding a month column
  mutate(month = month(date)) %>%
  select(date, month, zone, burn_status, everything()) %>%
  group_by(month) %>%
  mutate(mean_sd_bymonth_cm = mean(maxsnowdepth_cm)) %>%
  ungroup() %>%
  filter(month >= 2 & month <= 6)
```

Plotting

Weather Station Data

```{r}
#burned weather station snowdepths 
burned_wxsd_boxplot <- ggplot()+
  geom_boxplot(data = f_dailymax_persb_snow_wxstation, aes(x = factor(month), y = maxsnowdepth_cm, fill = "Persistent Zone"), alpha = 1) +
  geom_boxplot(data = f_dailymax_transb_snow_wxstation, aes(x = factor(month), y = maxsnowdepth_cm, fill = "Transitional Zone"), alpha = 0.7) +
  labs(
    title = "A. Burned Wx Station",
    x = "Month",
    y = "Snow Depth (cm)"
  ) +
  scale_fill_manual(name = "Snow Zone", values = c("Persistent Zone" = "#D95F02", "Transitional Zone" = "#66A61E")) +
  theme_bw()

burned_wxsd_boxplot

#unburned wx station boxplots
unburned_wxsd_boxplot <- ggplot()+
  geom_boxplot(data = f_dailymax_persub_snow_wxstation, aes(x = factor(month), y = maxsnowdepth_cm, fill = "Persistent Zone"), alpha = 1) +
  geom_boxplot(data = f_dailymax_transub_snow_wxstation, aes(x = factor(month), y = maxsnowdepth_cm, fill = "Transitional Zone"), alpha = 0.7) +
  labs(
    title = "C. Unburned Wx Station",
    x = "Month",
    y = "Snow Depth (cm)"
  ) +
  scale_fill_manual(name = "Snow Zone", values = c("Persistent Zone" = "#D95F02", "Transitional Zone" = "#66A61E")) +
  theme_bw()

unburned_wxsd_boxplot
```

Snow Camera Data

```{r}
#burned snow camera snowdepths 
burned_camerasd_boxplot <- ggplot()+
  geom_boxplot(data = f_dailymax105E_persb_snow, aes(x = factor(month), y = maxsnowdepth_cm, fill = "Persistent Zone"), alpha = 1) +
  geom_boxplot(data = f_dailymax105E_transb_snow, aes(x = factor(month), y = maxsnowdepth_cm, fill = "Transitional Zone"), alpha = 0.7) +
  labs(
    title = "B. Burned Camera",
    x = "Month",
    y = "Snow Depth (cm)"
  ) +
  scale_fill_manual(name = "Snow Zone", values = c("Persistent Zone" = "#D95F02", "Transitional Zone" = "#66A61E")) +
  theme_bw()

burned_camerasd_boxplot

#burned snow camera snowdepths 
unburned_camerasd_boxplot <- ggplot()+
  geom_boxplot(data = f_dailymax_persub_snow_wxstation, aes(x = factor(month), y = maxsnowdepth_cm, fill = "Persistent Zone"), alpha = 1) +
  geom_boxplot(data = f_dailymax105E_transub_snow, aes(x = factor(month), y = maxsnowdepth_cm, fill = "Transitional Zone"), alpha = 0.7) +
  labs(
    title = "D. Unburned Camera",
    x = "Month",
    y = "Snow Depth (cm)"
  ) +
  scale_fill_manual(name = "Snow Zone", values = c("Persistent Zone" = "#D95F02", "Transitional Zone" = "#66A61E")) +
  theme_bw()

unburned_camerasd_boxplot
```

Arranging Plots

```{r}
arranged_sd_boxplots <- ggarrange(
  burned_wxsd_boxplot,  burned_camerasd_boxplot, unburned_wxsd_boxplot, unburned_camerasd_boxplot, 
  ncol = 2, nrow = 2,  # Arrange in 2 columns and 2 rows
  common.legend = TRUE,  # Optionally share a common legend
  legend = "right"  # Position the legend at the bottom
)

arranged_sd_boxplots
```

```{r}
#saving the arranged boxplot
# Save the final plot
ggsave(
  filename = "arranged_sd_boxplots.png", 
  plot = arranged_sd_boxplots,  # Plot to save
  width = 10,  # Width of the plot in inches
  height = 8,  # Height of the plot in inches
  dpi = 300,  # Resolution in dots per inch
  units = "in"  # Units for width and height
)
```

## Weather Station-only Line Plots

For the months of February-June

```{r}
#creating filtered dataframes with daily means only of snowdepths

f_dailymean_transb_snow_wxstation <- full24_transb_snow_wxstation_data %>%
  mutate(month = month(date)) %>%
  #adding in burn_status and zone columns
  mutate(burn_status = "burned", zone = "transitional") %>%
  filter(month >= 2 & month <= 6) %>%
  group_by(date) %>%
  mutate(meansnowdepth_m = mean(SnowDepth_m, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(meansnowdepth_cm = meansnowdepth_m*100, na.rm = TRUE) %>%
  group_by(month)%>%
  mutate(mean_depth_bymonth_cm = mean(meansnowdepth_cm)) %>%
  ungroup() %>%
  group_by(date, month, zone, burn_status, meansnowdepth_m, meansnowdepth_cm, mean_depth_bymonth_cm)%>%
  summarize()

f_dailymean_transub_snow_wxstation <- full24_transub_snow_wxstation_data %>%
  mutate(month = month(date)) %>%
  #adding in burn_status and zone columns
  mutate(burn_status = "burned", zone = "transitional") %>%
  filter(month >= 2 & month <= 6) %>%
  group_by(date) %>%
  mutate(meansnowdepth_m = mean(SnowDepth_m, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(meansnowdepth_cm = meansnowdepth_m*100, na.rm = TRUE) %>%
  group_by(month)%>%
  mutate(mean_depth_bymonth_cm = mean(meansnowdepth_cm)) %>%
  ungroup() %>%
  group_by(date, month, zone, burn_status, meansnowdepth_m, meansnowdepth_cm, mean_depth_bymonth_cm)%>%
  summarize()

f_dailymean_persb_snow_wxstation <- full24_persb_snow_wxstation_data %>%
  mutate(month = month(date)) %>%
  #adding in burn_status and zone columns
  mutate(burn_status = "burned", zone = "transitional") %>%
  filter(month >= 2 & month <= 6) %>%
  group_by(date) %>%
  mutate(meansnowdepth_m = mean(SnowDepth_m, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(meansnowdepth_cm = meansnowdepth_m*100, na.rm = TRUE) %>%
  group_by(month)%>%
  mutate(mean_depth_bymonth_cm = mean(meansnowdepth_cm)) %>%
  ungroup() %>%
  group_by(date, month, zone, burn_status, meansnowdepth_m, meansnowdepth_cm, mean_depth_bymonth_cm)%>%
  summarize()

f_dailymean_persub_snow_wxstation <- full24_persub_snow_wxstation_data %>%
  mutate(month = month(date)) %>%
  #adding in burn_status and zone columns
  mutate(burn_status = "burned", zone = "transitional") %>%
  filter(month >= 2 & month <= 6) %>%
  group_by(date) %>%
  mutate(meansnowdepth_m = mean(SnowDepth_m, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(meansnowdepth_cm = meansnowdepth_m*100, na.rm = TRUE) %>%
  group_by(month)%>%
  mutate(mean_depth_bymonth_cm = mean(meansnowdepth_cm)) %>%
  ungroup() %>%
  group_by(date, month, zone, burn_status, meansnowdepth_m, meansnowdepth_cm, mean_depth_bymonth_cm)%>%
  summarize()
```

```{r}
#creating monthly dataframes with mean_monthly_snowdepth for points on plot
monthly_mean_persb_snow_wxstation <- f_dailymean_persb_snow_wxstation %>%
  group_by(month, zone, burn_status, mean_depth_bymonth_cm) %>%
  summarize() %>%
  #adding in a mid-month date column so that the it can be plotted on the same x-axis as line plots
  mutate(date = ymd(paste0("2024-", month, "-15")))

monthly_mean_persub_snow_wxstation <- f_dailymean_persub_snow_wxstation %>%
  group_by(month, zone, burn_status, mean_depth_bymonth_cm) %>%
  summarize() %>%
  #adding in a mid-month date column so that the it can be plotted on the same x-axis as line plots
  mutate(date = ymd(paste0("2024-", month, "-15")))

monthly_mean_transb_snow_wxstation <- f_dailymean_transb_snow_wxstation %>%
  group_by(month, zone, burn_status, mean_depth_bymonth_cm) %>%
  summarize() %>%
  #adding in a mid-month date column so that the it can be plotted on the same x-axis as line plots
  mutate(date = ymd(paste0("2024-", month, "-15")))

monthly_mean_transub_snow_wxstation <- f_dailymean_transub_snow_wxstation %>%
  group_by(month, zone, burn_status, mean_depth_bymonth_cm) %>%
  summarize() %>%
  #adding in a mid-month date column so that the it can be plotted on the same x-axis as line plots
  mutate(date = ymd(paste0("2024-", month, "-15")))
```

Plotting

-   This plot looks good! It is only using the weather station data though, something to consider!

```{r}
wx_dailyavg_sd_plot <- ggplot() +
  geom_line(data = f_dailymean_transb_snow_wxstation, 
            aes(x = date, y = meansnowdepth_cm, color = "Transitional", linetype = "Burned")) + 
  geom_line(data = f_dailymean_transub_snow_wxstation, 
            aes(x = date, y = meansnowdepth_cm, color = "Transitional", linetype = "Unburned")) + 
  geom_line(data = f_dailymean_persb_snow_wxstation, 
            aes(x = date, y = meansnowdepth_cm, color = "Persistent", linetype = "Burned")) + 
  geom_line(data = f_dailymean_persub_snow_wxstation, 
            aes(x = date, y = meansnowdepth_cm, color = "Persistent", linetype = "Unburned")) +
  #adding in points for the monthly mean snowdepths
  geom_point(data = monthly_mean_persb_snow_wxstation, 
             aes(x = date, y = mean_depth_bymonth_cm, color = "Transitional Weather Station", shape = "Burned"), size = 2) +
  geom_point(data = monthly_mean_persub_snow_wxstation, 
             aes(x = date, y = mean_depth_bymonth_cm, color = "Transitional Weather Station", shape = "Unburned"), size = 2) +
  geom_point(data = monthly_mean_transb_snow_wxstation, 
             aes(x = date, y = mean_depth_bymonth_cm, color = "Persistent Weather Station", shape = "Burned"), size = 2) +
  geom_point(data = monthly_mean_transub_snow_wxstation,
             aes(x = date, y = mean_depth_bymonth_cm, color = "Persistent Weather Station", shape = "Unburned"), size = 2) +
  labs(
    x = "Date",
    y = "Mean Daily Snowdepth (cm)",
    title = "Mean Daily Averaged Snow Depths by Zone and Burn Status", 
    color = "Snow Zone",  # Rename color legend
    linetype = "Burn Status", # Rename linetype legend
    shape = "Monthly Mean Depth (cm)"# Rename linetype legend"
  ) +
  theme_bw() +
  scale_color_manual(values = c("Persistent" = "#D95F02", "Transitional" = "#66A61E")) +
  scale_linetype_manual(values = c("Burned" = "solid", "Unburned" = "dashed")) +
  theme(legend.position = "right")

wx_dailyavg_sd_plot
```

```{r}
#saving plot
ggsave(
  filename = "wxstation_dailyavg_sd_plot.png", 
  plot = wx_dailyavg_sd_plot,  # Plot to save
  width = 10,  # Width of the plot in inches
  height = 8,  # Height of the plot in inches
  dpi = 300,  # Resolution in dots per inch
  units = "in"  # Units for width and height
)
```

\*\* need to find this saved plot and add it to the plot folde rin my r_folder. Then save and export changes to github.
